---
title: "Week 3 assignment plotly"
author: "Stefaan Delanghe"
date: "10/19/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
```

## Airports Belgium

The goal of this assignment is to plot all possible airports in Belgium. Aside from the international airport we have medium and small airports that surve as landing strips.

With a many thanks to HDX for the provision of the data set
[HDX](https://data.humdata.org/dataset/ourairports-bel)

Here follows a list of what we will do with the data.

- download the airports from Belgium.
- clean and tidy up the data.
- plot the airports on a ploty graph.

## Download data
### Here we download the file from HDX website.
```{r download, echo = TRUE, cache=TRUE}
download.file("http://ourairports.com/countries/BE/airports.hxl", 
              destfile = "be-airports.csv")
```

### Now we clean and tidy up the data
```{r tidy, echo = TRUE}
airports <- read.csv("be-airports.csv", header = T)
airportNames <- c("longitude_deg", "latitude_deg", "name")
col.num <- which(colnames(airports) %in% airportNames)
airportMarkers <- data.frame(airports[,col.num])
airportMarkers <- airportMarkers[-1,]
airportMarkers <- rename(airportMarkers, 
        c("latitude_deg"="lat", "longitude_deg"="lng", "name"="popup"))
```
airportMarkers contains the data for belgium airports and will be used to plot.

## Plot airports in plotly

```{r plot, echo = FALSE,message=FALSE}
library(plotly)
set.seed(12345)
plot_ly(data = airportMarkers, x = ~lat, y = ~lng,
  marker = list(size = 10,
                       color = 'rgba(255, 182, 193, .9)',
                       line = list(color = 'rgba(152, 0, 0, .8)',
                                   width = 2))) %>%
  layout(title = 'Latitude longitude belgium airports.',
         yaxis = list(zeroline = FALSE),
         xaxis = list(zeroline = FALSE))
```
